Lifting CDCL to Relational Domains

### 2016-10-15 deductions.tex
refactoring domain.tex figure 2

\section{Abstract Model Search}
%
\begin{figure}[t]
\scriptsize
\begin{tabular}{l|l|l}
\hline
C program & SSA & Octagon \\
\hline
\begin{lstlisting}[mathescape=true,language=C]
int main() {
 unsigned x, y;
 __CPROVER_assume(x==y);
 x++;
 assert(x==y+1);
}
\end{lstlisting}
&
\begin{minipage}{4.40cm}
$\begin{array}{l@{\,\,}c@{\,\,}l}
SSA &\iff& ((guard0 == TRUE) \land \\
    &    & (cond == (x == y)) \land \\
    &    & (guard1 == (cond \&\& guard0)) \land \\
    &    & (x' == 1u + x) \land \\
    &    & (x' == 1u + y || !guard1))
\end{array}$
\end{minipage}
&
\begin{minipage}{3.75cm}
$\begin{array}{l@{\,\,}c@{\,\,}l}
C &\iff& ((x' > 1) \land (-x'-y < -2) \land \\
  &    & (-x-x' < -2) \land (y-x' < 0) \land \\                                                                
  &    & (x-x' < 0) \land (y > 0) \land \\
  &    & (x > 0) \land (-x'-y < 0) \land \\
  &    & (x+y > 1) \land (y-x < 1) \land \\
  &    & (x'-y < 2) \land (x-y < 1) \land \\
  &    & (x+y > 0) \land (x+x' > 0) \land \\
  &    & (x'-x < 2))
\end{array}$
\end{minipage}
\\
\hline
\end{tabular}
\caption{C Program, corresponding SSA and Octagonal Inequalities}
\label{swssa}
\end{figure}
%
%    
\begin{algorithm2e}[t]
\DontPrintSemicolon
\SetKwFunction{deduce}{deduce}
\SetKwFunction{print}{print}
\SetKwFunction{return}{return}
\SetKwFunction{continue}{continue}
\SetKwFunction{assign}{assign}
\SetKwData{sat}{SAT}
\SetKwData{conflict}{CONFLICT}
\SetKwData{unsat}{UNSAT}
\SetKwData{unknown}{UNKNOWN}
\SetKwData{true}{true}
\SetKwInOut{Input}{input}
\SetKwInOut{Output}{output}
\SetKwFor{Loop}{Loop}{}{}
\SetKw{KwNot}{not}
\begin{small}
\Input{Set $S$ of $\widehat{ded_{\varphi}}$ for $\varphi$ over Abstract domain $A$,
abstract valuation $v$, propagation trail $\mathcal{T}$, reason trail $\mathcal{R}$}
\Output{The status (\sat or \conflict or \unknown)}
worklist $\leftarrow$ initialize\_worklist($S$) \;
\Loop{}
{
// Greatest fixed point \;
\While{$!worklist.empty()$} 
{
  $\langle live\_vars, s \rangle \leftarrow$ worklist.pop() \;
  $\mathit{meet\_irrd} \leftarrow$ domain(s, live\_vars, $v$)\;
  \uIf{$meet\_irrd == \bot$} {
    $\mathcal{R}[\bot] \leftarrow s$ \;
    worklist.delete() \;
    \return \conflict \;
  }
  \uElse
  {
    $\mathcal{T} \leftarrow \mathcal{T} . \mathit{meet\_irrd}$ \; 
    $v \leftarrow v \meet \mathit{meet\_irrd}$ \; 
    $\mathcal{R}[|\mathcal{T}|] \leftarrow s$ \;
    worklist.update(v, s) \; 
  }
}
\uIf{$v$ is $\gamma$-complete} {
  \return \sat;
}
\uElse {
 \return \unknown \;
}
}
\end{small}
\caption{Abstract Model Search $\langle deduce(S,v,\mathcal{T},\mathcal{R}) \rangle$ \label{Alg:ms}}
\end{algorithm2e}
%  
A model search procedure in a SAT solver involves two steps -- {\em deductions} 
using unit rule refines current partial assignments and 
{\em decisions} to heuristically guess a value for an unassigned 
literal.  A unit rule overapproximates a model transformer and deduction 
computes a greatest fixed point over the partial assignments
domain~\cite{dhk2013-popl}.  We present an abstract model search procedure 
that computes a greatest fixed point over meet irreducible deduction 
transformer in $S$.  
%

@@

\pscmt{give an example for $ded$}

\pscmt{define $ded$ for all statements}

>>>>

\section{Abstract Model Search}
%
\begin{figure}[t]
\scriptsize
\begin{tabular}{l|l|l}
\hline
C program & SSA & Octagon \\
\hline
\begin{lstlisting}[mathescape=true,language=C]
int main() {
 unsigned x, y;
 __CPROVER_assume(x==y);
 x++;
 assert(x==y+1);
}
\end{lstlisting}
&
\begin{minipage}{4.40cm}
$\begin{array}{l@{\,\,}c@{\,\,}l}
SSA &\iff& ((g0 == TRUE) \land \\
    &    & (cond == (x == y)) \land \\
    &    & (g1 == (cond \&\& guard0)) \land \\
    &    & (x' == 1u + x) \land \\
    &    & (x' == 1u + y || !1))
\end{array}$
\end{minipage}
&
\begin{minipage}{3.75cm}
$\begin{array}{l@{\,\,}c@{\,\,}l}
C &\iff& ((x' > 1) \land (-x'-y < -2) \land \\
  &    & (-x-x' < -2) \land (y-x' < 0) \land \\                                                                
  &    & (x-x' < 0) \land (y > 0) \land \\
  &    & (x > 0) \land (-x'-y < 0) \land \\
  &    & (x+y > 1) \land (y-x < 1) \land \\
  &    & (x'-y < 2) \land (x-y < 1) \land \\
  &    & (x+y > 0) \land (x+x' > 0) \land \\
  &    & (x'-x < 2))
\end{array}$
\end{minipage}
\\
\hline
\end{tabular}
\caption{C Program, corresponding SSA and Octagonal Inequalities}
\label{ssa}
\end{figure}
%
%    
\begin{algorithm2e}[t]
\DontPrintSemicolon
\SetKwFunction{deduce}{deduce}
\SetKwFunction{print}{print}
\SetKwFunction{return}{return}
\SetKwFunction{continue}{continue}
\SetKwFunction{assign}{assign}
\SetKwData{sat}{SAT}
\SetKwData{conflict}{CONFLICT}
\SetKwData{unsat}{UNSAT}
\SetKwData{unknown}{UNKNOWN}
\SetKwData{true}{true}
\SetKwInOut{Input}{input}
\SetKwInOut{Output}{output}
\SetKwFor{Loop}{Loop}{}{}
\SetKw{KwNot}{not}
\begin{small}
\Input{Set $S$ of $\widehat{ded_{\varphi}}$ for $\varphi$ over Abstract domain $A$,
abstract valuation $v$, propagation trail $\mathcal{T}$, reason trail $\mathcal{R}$}
\Output{The status (\sat or \conflict or \unknown)}
worklist $\leftarrow$ initialize\_worklist($S$) \;
\Loop{}
{
// Greatest fixed point \;
\While{$!worklist.empty()$} 
{
  $\langle live\_vars, s \rangle \leftarrow$ worklist.pop() \;
  $\mathit{meet\_irrd} \leftarrow$ domain(s, live\_vars, $v$)\;
  \uIf{$meet\_irrd == \bot$} {
    $\mathcal{R}[\bot] \leftarrow s$ \;
    worklist.delete() \;
    \return \conflict \;
  }
  \uElse
  {
    $\mathcal{T} \leftarrow \mathcal{T} . \mathit{meet\_irrd}$ \; 
    $v \leftarrow v \meet \mathit{meet\_irrd}$ \; 
    $\mathcal{R}[|\mathcal{T}|] \leftarrow s$ \;
    worklist.update(v, s) \; 
  }
}
\uIf{$v$ is $\gamma$-complete} {
  \return \sat;
}
\uElse {
 \return \unknown \;
}
}
\end{small}
\caption{Abstract Model Search $\langle deduce(S,v,\mathcal{T},\mathcal{R}) \rangle$ \label{Alg:ms}}
\end{algorithm2e}
%  
A model search procedure in a SAT solver involves two steps -- {\em deductions} 
using unit rule refines current partial assignments and 
{\em decisions} to heuristically guess a value for an unassigned 
literal.  A unit rule overapproximates a model transformer and deduction 
computes a greatest fixed point over the partial assignments
domain~\cite{dhk2013-popl}.  We present an abstract model search procedure 
that computes a greatest fixed point over meet irreducible deduction 
transformer in $S$.  
%

@@

\pscmt{give an example for $ded$, link it to the reason trail}

\pscmt{define $ded$ for all statements, connect this to worklist}

\pscmt{link livevars to $L$ -- the subdomain spanned by livevars}

### 2016-10-15 domains.tex
refactoring domain.tex figure 2

%-------------------------------------------------------------------------------
\subsection{Program Representation}

\begin{wrapfigure}{r}{3cm}
\[
\begin{array}{rcl}
g_0 &=& \true \\
\multicolumn{3}{l}{0 \leq v\leq N} \\
g_1 &=& g_0\wedge c\\
x_0 &=& v \\
x_1 &=& -v \\
x_2 &=& g_1?x_0:x_1 \\
g_2 &=& g_1 \vee g_0\wedge \neg c\\
z &=& x_2 * x_2 \\
\multicolumn{3}{l}{z<0 \wedge g_2}
\end{array}
\]
\caption{\label{fig:ssa}
SSA for the example in Figure~\ref{fig:example}
}
\end{wrapfigure}

We consider loop-free programs (respectively bounded unwindings of
programs with loops or recursion) with safety properties given as
assertions in the code.
%
Such a program is represented as set $\mathcal{P}$ of
\emph{statements} $s$.  These are constraints as typically obtained by
translating the program into single static assignment (SSA) form via a
data flow analysis.
%
Figure~\ref{fig:ssa} shows the constraints for the example program in
Figure~\ref{fig:example}.
%
Assignments such as \texttt{x=v;} become equalities $x_1=v$ where the
left-hand side variable gets a fresh name (subscript).
%
Control flow is encoded into guard variables such as $g_1=g_0\wedge c$.
%
Data flow joins become conditional expressions, e.g.\ $x_3=g_1?x_1:x_2$.
%
Assertions $\mathcal{A}$ are constraints $a$ of the form $g_3
\Rightarrow z\geq 0$, meaning that if $g_3$ holds (i.e.\ the assertion
is reachable) then the assertion must hold.

%For example, figure~\ref{swssa} presents the program analysis constraints for 
%a C program in Static Single Assignment (SSA) form.

@@

%-------------------------------------------------------------------------------
\subsection{Abstract Domain}
%-------------------------------------------------------------------------------
The results that we present on lifting ACDL to relational domains hold
for any relational domain.
% 
In our prototype implementation and for illustrative purposes in this
paper we use a product domain $\mathcal{B}^b\times\mathcal{R}$ where
$\mathcal{B}$ is the partial Boolean assignments domain
$\langle\{\true,\false,\bot,\top\},\Rightarrow,\wedge,\vee\rangle$ (as
used in SAT solvers~\cite{sas12}), $b$ is the number of Boolean
variables in the program, and $\mathcal{R}$ is a \emph{relational}
domain over the numerical (bitvector) variables in their respective
data types (currently, signed and unsigned integers are supported).
%
We instantiate $\mathcal{R}$ with the template polyhedra domain.

@@

%-------------------------------------------------------------------------------
\subsection{Properties of Abstract Domains for Learning}
%-------------------------------------------------------------------------------
%
An important property of a clause learning SAT solver is that each
element of the partial Boolean assignments domain is decomposable into
complementable elements.  This property of the domain is required to
learn elements that help to guide the model search away from the
conflicting region of the search space.
%
Most numerical abstract domains, such as intervals and octagons lack
complements, but they can be represented as intersections of
complementable half-spaces, each of which has a complement. We
formalise this in the sequel.

\begin{definition} 
A \emph{meet irreducible} $m$ 
in a complete lattice structure $A$ is an element with the following property.
\[\forall m_1, m_2 \in A: m_1 \meet m_2 = m \implies (m = m_1 \lor m = m_2), m \neq \top \]  
\end{definition}

The meet irreducibles in the partial Boolean assignments domain
$\mathcal{B}$ are $\true$ and $\false$. The meet irreducibles in the
template polyhedra domain are all elements that concretise to
half-spaces, i.e.\ they can be represented by a single inequality. For
the interval domain, these are \ $x \leq d$ or $x \geq d$ for
constants $d$.

@@

For polyhedra this intuitively means that each polyhedron can be
written as an intersection of half-spaces.
%
For example, the meet decomposition of the interval domain element
% $(x,y) \in [2,4]\times[3, 5]$ 
$2\leq x\leq 4 \wedge 3\leq y\leq 5$ is
the set $\{x\geq 2, x\leq 4, y\geq 3, y\leq 5\}$.
% \langle x:[2, 4] \rangle \in ItvDom$ which gives set of meet irreducibles, 
% $\{ \langle y \succeq 3 \rangle, \langle y \preceq 5 \rangle, 
% \langle x \succeq 2 \rangle, \langle x \preceq 4 \rangle \}$, that are 
% precisely complementable.

@@

The meet irreducibles in the partial Boolean assignments domain and
template polyhedra domains are all complementable.
%
Note that for template polyhedra, all non-meet-irreducible elements $e$
(except $\bot$ and $\top$) are not complementable within $A$.
%
However, we can complement each element in the meet decomposition of $e$ and
re-interpret the obtained set as a disjunction. 
%
Thus the complement of the octagon in Figure~\ref{octagon} 
can be written as a disjunction of meet irreducibles:
\[(x\leq -3) \lor (x\geq 2) \lor (y\leq -2) \lor (y\geq 3) \lor (x+y\geq 3) \lor (x-y\geq 2) \lor (y-x\geq 4) \lor (-x-y\geq 3)\]

Standard abstract interpretation does not require complementation property.  
Abstract Domain library, such as APRON C library~\cite{apron} is specialized 
for abstract interpretation.  We implement a template-based polyhedra domain 
that returns precise complements by decomposing it into half-spaces.

@@

\Omit{
%
An important property of a clause learning SAT solver 
is that a partial assignments domain can be decomposed 
into a set of precisely complementable singleton assignments.  
This property of the partial assignments domain helps to 
guide the model search away from the conflicting region 
of the search space and allows case-based analysis.  
%
\begin{definition}{(Precise complement)} A precise complement of an abstract
element $a \in A$ in abstract lattice $A$ is an element $\bar{a}$ such that 
$\gamma(\bar{a} = \neg \gamma(a))$.
\end{definition}
%
The precise complementation property of partial assignment lattice 
can be generalized to other lattice structures.  Most numerical 
abstract domains, such as intervals, octagons, polyhedra, can be 
decomposed into half-spaces, that admits precise complements.  
For example, intervals lack complements, but the meet decomposition 
of intervals into meet-irreducibles have precise complements.  
Numerical abstract domains that admit complementable decomposition 
are shown in Figure~\ref{complement}.  Our template-based domain 
implementation precisely complements a meet irreducible in an abstraction.
% 
\begin{table}
\begin{center}
{
\begin{tabular}{l|l}
\hline
Domain & Precise Complements \\ \hline 
Interval & \((x \leq n) \quad \longrightarrow (x > n)\) \\ \hline
Octagon & \((x+y < 1) \quad \longrightarrow (-x-y < 0)\) \\ \hline
Equality & \((x==y) \quad \longrightarrow (x \neq y)\) \\ \hline 
\end{tabular}
}
\end{center}
\label{fig:complement}
%\caption{C Program, Control-flow Graph (CFG) and Abstract Conflict Graph}
\end{table}
}
% \Omit {
% The commonly used library for numerical abstract domains  
% is the APRON C library~\cite{apron}.  This library is 
% used for the static analysis of the numerical variables 
% of a program by abstract interpretation. APRON provides a 
% C API interface to various abstract domains and libraries 
% such as {\em BOX}, {\em OCTAGON}, {\em Convex Polyhedra} and
% {\em Linear Equalities} library.  The aim of such analysis is 
% to compute invariants over numerical variables in the 
% program~\cite{se2011}. 
% }
% \Omit {
% To this end, we implement our own template-based polyhedra domain and interval 
% domain which supports complementation operator.  
% %For example, the octagon in Figure~\ref{octagon} can be written as a conjunction of:
% %\[(x>=-2) \land (x<=1) \land (y>=-1) \land (y<=2) \land (x+y<=2)
% %\land (x-y<=1) \land (y-x<=3) \land (-x-y<=2)\] 
% \pscmt{That's no valid motivation. We never complement a whole octagon, but just a
%  meet-irreducible. It's trivial to do that with APRON. The reason was
% a different one: APRON does not support all C operators, e.g. the bitwise
% operators.} 
% }

>>>>

%-------------------------------------------------------------------------------
\subsection{Program Representation}  
\Omit {
\begin{wrapfigure}{r}{3cm}
\[
\begin{array}{rcl}
g_0 &=& \true \\
\multicolumn{3}{l}{0 \leq v\leq N} \\
g_1 &=& g_0\wedge c\\
x_0 &=& v \\
x_1 &=& -v \\
x_2 &=& g_1?x_0:x_1 \\
g_2 &=& g_1 \vee g_0\wedge \neg c\\
z &=& x_2 * x_2 \\
\multicolumn{3}{l}{z<0 \wedge g_2}
\end{array}
\]
\caption{\label{fig:ssa}
SSA for the example in Figure~\ref{fig:example}
}
\end{wrapfigure}
}
\begin{figure}[t]
\scriptsize
\begin{tabular}{l|l}
\hline
 SSA & Octagon \\
\hline
\begin{minipage}{4.20cm}
$\begin{array}{rcl}
(g_0 = \true) \wedge (c = 0 \leq v\leq N) \\
(g_1 = g_0 \wedge c) \wedge (x_0 = v) \wedge \\
(x_1 = -v) \wedge (x_2 = g_1?x_0:x_1) \wedge \\
(g_2 = g_1 \vee g_0\wedge \neg c) \wedge \\
(z  = x_2 * x_2) \wedge (z<0 \wedge g_2)
\end{array}$
\end{minipage}
&
\begin{minipage}{4.50cm}
$\begin{array}{l@{\,\,}c@{\,\,}l}
C &\iff& ((x \geq -5) \land (x \leq 5) \land \\
  &    & (z \geq 0) \land (z \leq 25) \land \\
  &    & (x-z \leq 5) \land (x-z \geq -30) \land \\
  &    & (x+z \geq -5) \land (x+z \leq 30))  
\end{array}$
\end{minipage}
\\
\hline
\end{tabular}
\caption{SSA and Octagonal Inequalities}
\label{ssa}
\end{figure}
%
We consider loop-free programs (respectively bounded unwindings of
programs with loops or recursion) with safety properties given as
assertions in the code.
%
Such a program is represented as set $\mathcal{P}$ of
\emph{statements} $s$.  These are constraints as typically obtained by
translating the program into single static assignment (SSA) form via a
data flow analysis.
%
Figure~\ref{ssa} shows the SSA constraints for the program in figure~\ref{fig:example}. 
%
Assignments such as \texttt{x=v;} become equalities $x_1=v$ where the
left-hand side variable gets a fresh name (subscript).
%
Control flow is encoded into guard variables such as $g_1=g_0\wedge c$.
%
Data flow joins become conditional expressions, e.g.\ $x_3=g_1?x_1:x_2$.
%
Assertions $\mathcal{A}$ are constraints $a$ of the form $g_3
\Rightarrow z\geq 0$, meaning that if $g_3$ holds (i.e.\ the assertion
is reachable) then the assertion must hold.
%
%
%
%For example, figure~\ref{swssa} presents the program analysis constraints for 
%a C program in Static Single Assignment (SSA) form.

@@

%-------------------------------------------------------------------------------
\subsection{Abstract Domain}
%-------------------------------------------------------------------------------
The work of~\cite{sas12,dhk2013-popl} shows that CDCL based SAT solvers 
operates on the partial assignment domains. We present a generic instantiation 
of CDCL architecture that can be extended to any relational and non-relational
domains.  
% 
In our prototype implementation and for illustrative purposes in this
paper we use a product domain $\mathcal{B}^b\times\mathcal{R}$ where
$\mathcal{B}$ is the Boolean domain
$\langle\{\true,\false,\bot,\top\},\Rightarrow,\wedge,\vee\rangle$, 
$b$ is the number of Boolean variables in the program, 
and $\mathcal{R}$ is a \emph{relational} domain over the 
numerical (bitvector) variables in their respective
data types (currently, signed and unsigned integers are supported).
%
We instantiate $\mathcal{R}$ with the template polyhedra domain.

@@

%-------------------------------------------------------------------------------
\subsection{Properties of Abstract Domains}
%-------------------------------------------------------------------------------
%
\Omit {
An important property of a clause learning SAT solver is that each
element of the partial assignments domain is decomposable into
complementable elements.  This property of the domain is required to
learn elements that help to guide the model search away from the
conflicting region of the search space.
%
Most numerical abstract domains, such as intervals and octagons lack
complements, but they can be represented as intersections of
complementable half-spaces, each of which has a complement. 
}

We identify specific properties of domain elements necessary for 
abstract model search and learning in abstractions.  We formalise 
this in the sequel.
%
\begin{definition} 
A \emph{meet irreducible} $m$ in a complete lattice 
structure $A$ is an element with the following property.
\[\forall m_1, m_2 \in A: m_1 \meet m_2 = m \implies (m = m_1 \lor m = m_2), m \neq \top \]  
\rmcmt{mention minimum complementable element}
\end{definition}
%
The meet irreducibles in boolean domain $\mathcal{B}$ are 
$\{x \mapsto \true\}$ and $\{x \mapsto \false\}$. The meet 
irreducibles in the template polyhedra domain are all elements 
that concretise to half-spaces, i.e.\ they can be represented 
by a single inequality. For the interval domain, these are 
\ $x \leq d$ or $x \geq d$ for constants $d$.

@@

For polyhedra this intuitively means that each polyhedron can be
written as an intersection of half-spaces.
%
For example, the meet decomposition of the interval domain element
% $(x,y) \in [2,4]\times[3, 5]$ 
$decomp(2\leq x\leq 4 \wedge 3\leq y\leq 5)$ is
the set $\{x\geq 2, x\leq 4, y\geq 3, y\leq 5\}$.
% \langle x:[2, 4] \rangle \in ItvDom$ which gives set of meet irreducibles, 
% $\{ \langle y \succeq 3 \rangle, \langle y \preceq 5 \rangle, 
% \langle x \succeq 2 \rangle, \langle x \preceq 4 \rangle \}$, that are 
% precisely complementable.

@@

An important property of a clause learning SAT solver 
is that a partial assignments domain can be decomposed 
into a set of precisely complementable singleton assignments.  
This property of the partial assignments domain helps to 
guide the model search away from the conflicting region 
of the search space and allows case-based analysis.  Complementation 
operator in abstract domains is different from the notion of precise
complements. 
%
\begin{definition}{(Precise complement)} Let $A$ be an lattice. A precise 
complement of an abstract element $a \in A$ is an element $\bar{a} \in A$ 
such that the negation of concretization $(\gamma)$ of $a$ is equivalent to 
concretization of $\bar{a}$, that is, $\gamma(\bar{a}) = \neg \gamma(a))$.
\end{definition}
%
The precise complementation property of partial assignment lattice 
can be generalized to other lattice structures.  Most numerical 
abstract domains, such as intervals, octagons, polyhedra, can be 
decomposed into half-spaces, that admits precise complements.  
For example, intervals lack complements, but the meet decomposition 
of intervals into meet-irreducibles have precise complements.  
Numerical abstract domains that admit complementable decomposition 
are shown in Figure~\ref{complement}.  Our template-based domain 
implementation precisely complements a meet irreducible in an abstraction.
% 
\begin{table}
\begin{center}
{
\begin{tabular}{l|l}
\hline
Domain & Precise Complements \\ \hline 
Interval & \((x \leq n) \quad \longrightarrow (x > n)\) \\ \hline
Octagon & \((x+y < 1) \quad \longrightarrow (-x-y < 0)\) \\ \hline
Equality & \((x==y) \quad \longrightarrow (x \neq y)\) \\ \hline 
\end{tabular}
}
\end{center}
\label{fig:complement}
\end{table}

\Omit {
The meet irreducibles in the partial Boolean assignments domain and
template polyhedra domains are all complementable.
%
Note that for template polyhedra, all non-meet-irreducible elements $e$
(except $\bot$ and $\top$) are not complementable within $A$.
%
However, we can complement each element in the meet decomposition of $e$ and
re-interpret the obtained set as a disjunction. 
%
Thus the complement of the octagon in Figure~\ref{octagon} 
can be written as a disjunction of meet irreducibles:
\[(x\leq -3) \lor (x\geq 2) \lor (y\leq -2) \lor (y\geq 3) \lor (x+y\geq 3) \lor (x-y\geq 2) \lor (y-x\geq 4) \lor (-x-y\geq 3)\]

Standard abstract interpretation does not require complementation property.  
Abstract Domain library, such as APRON C library~\cite{apron} is specialized 
for abstract interpretation.  We implement a template-based polyhedra domain 
that returns precise complements by decomposing it into half-spaces.    
}

@@

\Omit{
%
}
% \Omit {
% The commonly used library for numerical abstract domains  
% is the APRON C library~\cite{apron}.  This library is 
% used for the static analysis of the numerical variables 
% of a program by abstract interpretation. APRON provides a 
% C API interface to various abstract domains and libraries 
% such as {\em BOX}, {\em OCTAGON}, {\em Convex Polyhedra} and
% {\em Linear Equalities} library.  The aim of such analysis is 
% to compute invariants over numerical variables in the 
% program~\cite{se2011}. 
% }
% \Omit {
% To this end, we implement our own template-based polyhedra domain and interval 
% domain which supports complementation operator.  
% %For example, the octagon in Figure~\ref{octagon} can be written as a conjunction of:
% %\[(x>=-2) \land (x<=1) \land (y>=-1) \land (y<=2) \land (x+y<=2)
% %\land (x-y<=1) \land (y-x<=3) \land (-x-y<=2)\] 
% \pscmt{That's no valid motivation. We never complement a whole octagon, but just a
%  meet-irreducible. It's trivial to do that with APRON. The reason was
% a different one: APRON does not support all C operators, e.g. the bitwise
% operators.} 
% }
